Nested sampling with multiple scalars

### 2015-09-29 Paper/ms.tex
Enumerate instead of itemize

We seek an algorithm for computing the partition function
$Z(\alpha_1, \alpha_2)$ for a range of values of the $\alpha$s, from a single
run. To be considered a variant of Nested Sampling, we require that the method
satisfies the following requirements:
\begin{itemize}
\item The algorithm should begin with $n$ points drawn from the prior $\pi(\xx)$.
\item The algorithm should seek to explore regions where the values of
$S_1(\xx)$ and $S_2(\xx)$ are greater than what would be expected from the
prior.
\item The algorithm should try to move through a sequence of probability
distributions whose enclosed prior masses are approximately known.
\item The algorithm should be invariant to monotonic transformations of
$S_1$ and $S_2$, i.e. it should only depend on rankings of $S_1$ and $S_2$
values and not the values themselves.
\end{itemize}

>>>>

We seek an algorithm for computing the partition function
$Z(\alpha_1, \alpha_2)$ for a range of values of the $\alpha$s, from a single
run. To be considered a variant of Nested Sampling, we require the method
to satisfy the following requirements:
\begin{enumerate}
\item The algorithm should begin with $N$ points drawn from the prior $\pi(\xx)$.
\item The algorithm should seek to explore regions where the values of
$S_1(\xx)$ and $S_2(\xx)$ are greater than what would be expected from the
prior.
\item The algorithm should try to move through a sequence of probability
distributions proportional to $\pi$, but restricted to smaller and smaller
domains for which we can approximately measure the enclosed prior mass.
\item The algorithm should be invariant to monotonic transformations of
$S_1$ and $S_2$, i.e. it should only depend on rankings of $S_1$ and $S_2$
values and not the values themselves.
\end{enumerate}
